Figures for 3-D printed oxygen devices

### 2015-03-04 publishing/latex/figures.tex
updated figure 2

\begin{figure}[H]
\includegraphics[scale=0.15]{fig2.png}
\caption{
{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device. Each 6 well row of the plate can be controlled independently.  
}
\label{figure2}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[scale=0.15]{fig2.png}
\caption{
{\bf Oxygen Characterization.} 
(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
Error bars are the standard deviation N=3.
(B) Four oxygen conditions are demonstrated in a 24-well plate.
Each 6-well row of the plate can be controlled independently.  
}
\label{figure2}
\end{figure}
